A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-17 paper/paper.Rmd
density plot instead of a scatterplot to compare experiences

```{r compare-xp-sw, fig.cap = "Males dropouts' work experience in the original and refreshed data. Each point represents the work experience of individuals (identified by the ID) in the corresponding survey period. We can see that the correlation is reasonably high between them even there are different values for many individuals.", out.width = "70%"}
```

@@

@@

There are two aspects of the original data that make the replication with exactly the same result is not obtained. The first one is that the calculation of the time variable provided, which is the "work experience", is not clearly articulated. @SingerJudithD2003Alda mention that the temporal variable is the years of experience since the first day of work. However, this exact same variable is not explicitly available in the database. From the NLSY79 topical guide [@nlsy79guide], we find that several variables are tagged as work experience-related variables. One of them is the weeks of worked since the last interview. Hence, we use this to calculate the variable. Even though we got different result, the correlation between the original and refreshed work experience is reasonably high as shown in Figure \ref{fig:compare-xp-sw}.

>>>>

@@

```{r compare-xp-sw, fig.cap = "Density plot comparing the calculated work experience in the refreshed data, up to 1994, with that of the original data for male dropouts. Experience is shown on a square root scale to reduce the skewness. The highest concentration of observations is along the x=y axis, which means that most observations at most time points are similar.", out.width = "70%"}
```

@@

There are two aspects of the original data that make the replication with exactly the same result is not obtained. The first is that the calculation of the work experience is not clearly articulated. @SingerJudithD2003Alda mention that the temporal variable is the years of experience since the first day of work. However, this exact same variable is not explicitly available in the database. From the NLSY79 topical guide [@nlsy79guide], we find that several variables are tagged as work experience-related variables. One of them is the weeks of worked since the last interview. This is used to calculate the variable. It produces similar results, as shown in Figure \ref{fig:compare-xp-sw}.

### 2022-02-17 paper/paper.tex
density plot instead of a scatterplot to compare experiences

\caption{Males dropouts' work experience in the original and refreshed data. Each point represents the work experience of individuals (identified by the ID) in the corresponding survey period. We can see that the correlation is reasonably high between them even there are different values for many individuals.}\label{fig:compare-xp-sw}
\end{figure}

@@

@@

There are two aspects of the original data that make the replication with exactly the same result is not obtained. The first one is that the calculation of the time variable provided, which is the ``work experience'', is not clearly articulated. Singer and Willett (2003) mention that the temporal variable is the years of experience since the first day of work. However, this exact same variable is not explicitly available in the database. From the NLSY79 topical guide (Bureau of Labor Statistics, U.S. Department of Labor 2021b), we find that several variables are tagged as work experience-related variables. One of them is the weeks of worked since the last interview. Hence, we use this to calculate the variable. Even though we got different result, the correlation between the original and refreshed work experience is reasonably high as shown in Figure \ref{fig:compare-xp-sw}.

>>>>

@@

\caption{Density plot comparing the calculated work experience in the refreshed data, up to 1994, with that of the original data for male dropouts. Experience is shown on a square root scale to reduce the skewness. The highest concentration of observations is along the x=y axis, which means that most observations at most time points are similar.}\label{fig:compare-xp-sw}
\end{figure}

@@

There are two aspects of the original data that make the replication with exactly the same result is not obtained. The first is that the calculation of the work experience is not clearly articulated. Singer and Willett (2003) mention that the temporal variable is the years of experience since the first day of work. However, this exact same variable is not explicitly available in the database. From the NLSY79 topical guide (Bureau of Labor Statistics, U.S. Department of Labor 2021b), we find that several variables are tagged as work experience-related variables. One of them is the weeks of worked since the last interview. This is used to calculate the variable. It produces similar results, as shown in Figure \ref{fig:compare-xp-sw}.
